Smartphones have become one of the most commonly used communication devices due to their improved connectivity, functionality, and productivity. As smart technologies continue to advance, new levels of potential risks emerge. The majority of the market relies on Android operating system phones, which holds a significant position in the competitive market, forming an Android-iOS duopoly. Android devices store a vast amount of data, which can be stored locally or remotely, providing forensic experts with reliable data that is crucial for forensic investigations.\\

The objective of this coursework is to develop a dynamic tool for data extraction, analysis, and preparation for forensic examination. The tool has been developed considering the fact that most existing tools are not compatible with all Android mobile devices. The tool has been programmed using the Shell Script language, utilizing commands that have been automated and divided into separate scripts, which facilitate forensic analysis. This tool can be used on Linux or Windows (with Windows Subsystem for Linux) operating systems. To access the data, ADB Shell communication is utilized on the root level, which can be achieved by booting into an unofficial recovery mode. During the development, considerations have been made for call log history, SMS messages, browser history, photos, and other files that are relevant to forensic examination. Data is organized into directories to facilitate further analysis.\\

The developed tool extracts the data partition image of the device, saves it, and properly formats the extracted data for convenient use in case resolution. This tool works with most Samsung devices that do not have the force encrypt feature enabled, and it can also be adapted for devices from other manufacturers.\\